Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-01-20 paper/ms.tex
normalization of astero plots

It turns out that this kernel function can be made even more general by
introducing complex parameters $a_j \to a_j+i\,b_j$ and $c_j \to c_j+i\,d_j$,
and taking the real component of this complex kernel.
In this case, the covariance function becomes
\begin{eqnarray}\eqlabel{celerite-kernel-complex}
k_\bvec{\alpha}(\tau_{nm}) = \sigma_n^2\,\delta_{nm} +
    \sum_{j=1}^J &&\left[
    \frac{1}{2}(a_j + i\,b_j)\,\exp\left(-(c_j+i\,d_j)\,\tau_{nm}\right)
        \right. \nonumber\\
    &&+\left.
    \frac{1}{2}(a_j - i\,b_j)\,\exp\left(-(c_j-i\,d_j)\,\tau_{nm}\right)
\right]
\end{eqnarray}
and, for this function, \eq{gp-likelihood} can still be solved with
$\mathcal{O}(J^2\,N)$ operations.
The details of this method and a few implementation considerations are
discussed in \app{implementation}.

>>>>

It turns out that this kernel function can be made even more general by
introducing complex parameters $a_j \to a_j\pm i\,b_j$ and
$c_j \to c_j\pm i\,d_j$.
In this case, the covariance function becomes
\begin{eqnarray}\eqlabel{celerite-kernel-complex}
k_\bvec{\alpha}(\tau_{nm}) = \sigma_n^2\,\delta_{nm} +
    \sum_{j=1}^J &&\left[
    \frac{1}{2}(a_j + i\,b_j)\,\exp\left(-(c_j+i\,d_j)\,\tau_{nm}\right)
        \right. \nonumber\\
    &&+\left.
    \frac{1}{2}(a_j - i\,b_j)\,\exp\left(-(c_j-i\,d_j)\,\tau_{nm}\right)
\right]
\end{eqnarray}
and, for this function, \eq{gp-likelihood} can still be solved with
$\mathcal{O}(J^2\,N)$ operations.
The details of this method and a few implementation considerations are
discussed in \app{implementation}.
